Dual selection games

### 2020-01-03 articles/dual-selection-games/article.tex
add line numbers
revise based on referee report

@@

  For brevity, let 
  \[
    \schStrongSelGame{\mc A}{\neg \mc B}
      =
    \schStrongSelGame{\mc A}{\mc P\left(\bigcup \mc A\right)\setminus \mc B}
  .\]
  That is, \(\plII\) wins in the case that \(\{B_n:n<\omega\}\not\in\mc B\),
  and \(\plI\) wins otherwise.

\begin{definition}
  For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
  be the collection of all choice functions on \(X\).
\end{definition}

@@

\begin{definition}
  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restrction of \(f\)
  to \(X\). In particular, for \(f\in B^\omega\) and \(n<\omega\), \(f\rest n\)
  describes the first \(n\) terms of the sequence \(f\).
\end{definition}

@@

\begin{definition}
  Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
  if player \(\plI\) has a winning
  strategy (resp. winning predetermined/constant strategy) for the game \(G\). Similarly,
  write \(\plII\win G\) (resp. \(\plII\markwin G\), \(\plII\tactwin G\)) 
  if player \(\plII\) has a winning
  strategy (resp. winning Markov/tactical strategy) for the game \(G\).
\end{definition}

@@

\begin{definition}
  The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
  that for each sequence \(\setB{A_n}{n<\omega}\in[\mc A]^\omega\),
  there exist \(B_n\in A_n\) such that \(\setB{B_n}{n<\omega}\in\mc B\).
\end{definition}

@@

\begin{definition}
  The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
  that for each \(A\in \mc A\), there exists a subset
  \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
\end{definition}

@@

In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
separability game introduced by Scheepers 
in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
were perfect-information dual in his paper.

@@

Let 
\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\). 
Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,
\(\Gamma_{C_p(X),\mathbf 0}\) as defined in Definition \ref{selectionSets}),
see e.g. \cite{BUKOVSKY2019239}.

>>>>

\usepackage{lineno}
\linenumbers

@@

  Let \(\mc P(Z)=\{z:z\subseteq Z\}\) denote the power set of \(Z\),
  so \(\{B_n:n<\omega\}\in\mc P(\bigcup\mc A)\) for any choices
  \(B_n\in A_n\in\mc A\) made by the players.
  Then for brevity, let 
  \[
    \schStrongSelGame{\mc A}{\neg \mc B}
      =
    \schStrongSelGame{\mc A}{\mc P\left(\bigcup \mc A\right)\setminus \mc B}
  .\]
  That is, this is the analogous game where
  \(\plII\) wins provided \(\{B_n:n<\omega\}\not\in\mc B\),
  and \(\plI\) wins otherwise.

\begin{notation}
  For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
  be the collection of all choice functions on \(X\).
\end{notation}

@@

\begin{notation}
  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restriction of \(f\)
  to \(X\). In particular, for \(f\in B^\omega\) and \(n<\omega\), \(f\rest n\)
  describes the first \(n\) terms of the sequence \(f\).
\end{notation}

@@

\begin{notation}
  Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
  if player \(\plI\) has a winning
  strategy (resp. winning predetermined/constant strategy) for the game \(G\). Similarly,
  write \(\plII\win G\) (resp. \(\plII\markwin G\), \(\plII\tactwin G\)) 
  if player \(\plII\) has a winning
  strategy (resp. winning Markov/tactical strategy) for the game \(G\).
\end{notation}

@@

\begin{definition}[\cite{MR1378387}]
  The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
  that for each sequence \(\setB{A_n}{n<\omega}\in[\mc A]^\omega\),
  there exist \(B_n\in A_n\) such that \(\setB{B_n}{n<\omega}\in\mc B\).
\end{definition}

@@

\begin{definition}[\cite{MR2363173}]
  The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
  that for each \(A\in \mc A\), there exists a subset
  \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
  (When \(\kappa\) is omitted, the criterion \(|B|=\kappa\) is also omitted.)
\end{definition}

@@

In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
separability game introduced by Scheepers 
in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
were perfect-information dual in \cite{MR1711901}.

@@

Let 
\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[\mc T_X]^{<\aleph_0})\}\). 
Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,
\(\Gamma_{C_p(X),\mathbf 0}\) as defined in Definition \ref{selectionSets}),
see e.g. \cite{BUKOVSKY2019239}.
